RNA-seq from 4 cell populations

### 2021-08-04 deconvolution/fans4/molec_profiling.Rmd
bug fix

>>>>

df_disease_de = lapply(levels(info$CellType), function(CT){

  tab = topTable( fitDisease, coef = key, number=Inf)
  tab$ensID = rownames(tab)
  tab$CellType = CT
  tab$se = with(tab, logFC / t)
  tab
  })
names(df_disease_de) = levels(info$CellType)
df_disease_de = do.call(rbind, df_disease_de)

B.hat = reshape2::dcast( df_disease_de, ensID ~ CellType, value.var='logFC')
rownames(B.hat) = B.hat$ensID
B.hat = as.matrix(B.hat[,-1])

se.hat = reshape2::dcast( df_disease_de, ensID ~ CellType, value.var='se')
rownames(se.hat) = se.hat$ensID
se.hat = as.matrix(se.hat[,-1])

mashObj = mash_set_data( B.hat, se.hat)

m.1by1 = mash_1by1(mashObj)
strong = get_significant_results(m.1by1, 0.05)

U.pca = cov_pca(mashObj,3,subset=strong)
print(names(U.pca))

U.ed = cov_ed(mashObj, U.pca, subset=strong)

U.c = cov_canonical(mashObj)  
resMash = mash(mashObj, c(U.c,U.ed))

plotCorrMatrix(cor(resMash$result$PosteriorMean))
```

```{r upset.mashr}
lst = fromList(apply(resMash$result$lfsr, 2, function(x) names(x[x < 0.05])))

a = upset(lst, keep.order = FALSE, order.by="freq" )
